---
title: "HackathonCS"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r}
library(tidyverse)
library(car)
library(rpart)
library(rpart.plot)
library(nnet)
library(randomForest)
library(effects)
library(nnet)
# library BCA required
```

## Data Wrangling

* Reading CSV Files

```{r}
library(readr)
Retention2017 <- read_csv("Retention2017R.csv")
head(Retention2017)
```

* Transforming date variables

```{r}
Retention2017$lost <- as.factor(Retention2017$lost)
```

* Convert variables

```{r}
Retention2017$created <- as.Date(Retention2017$created,format = "%d/%m/%Y")
```

* Counting Missing Variables

```{r}
summary(Retention2017)
```

* Handle missing values: missing values should be handled 
  differently depending on the situation (Why do we want to 
  handle the missing values in the following variables 
  in the shown method?)

```{r}
Retention2017 <- Retention2017[!is.na(Retention2017$firstorder),]
Retention2017 <- mutate(Retention2017, NA_eclickrate = ifelse(is.na(eclickrate) == 1,1,0))
Retention2017$eclickrate[Retention2017$NA_eclickrate == 1] <- 0
```

  * (eclickrate can be NA if the customer never received emails 
    or received emails that never had links)

```{r}
Retention2017 <- mutate(Retention2017, NA_refill_doorstep = ifelse(is.na(refill) == 1,1,0))
Retention2017$refill[Retention2017$NA_refill_doorstep == 1] <- "N"
Retention2017$doorstep[Retention2017$NA_refill_doorstep == 1] <- "N"
```

  * (Refill and doorstep: When NA values occur in the same record, 
    the customers could have never been offered these options)

* Create new variables

```{r}
Retention2017$cust_period = as.Date(Retention2017$lastorder, format="%d/%m/%Y") - as.Date(Retention2017$firstorder, format="%d/%m/%Y") 
```

* Merge two datasets (Although the 2017 case doesn’t require this, 
  knowing the inner (I) join, outer (O) join, left (L) and 
  right (R) join may come in handy)

```{r}
#Retention2017_I <- inner_join(x = Retention2017, y=new, by = "custid") 
#Retention2017_O <- merge(x = Retention2017, y=new, by = "custid", all = TRUE)
#Retention2017_L <- merge(x = Retention2017, y=new, by = "custid", all.x = TRUE)
#Retention2017_R <- merge(x = Retention2017, y=new, by = "custid", all.y = TRUE)
  
  ## 'new', a second dataset, does not exist
```


## Model Building

* Running a classification tree

```{r}
Model1.RPart <- rpart(formula = lost~
                        eopenrate
                        +eclickrate
                        +avgorder
                        +ordfreq
                        +paperless
                        +refill
                        +doorstep
                        +favday
                        +city
                        +cust_period,
                        data = filter(Retention2017, Sample == "Estimation"),
                        cp = 0.01,
                        model = TRUE)
plotcp(Model1.RPart)
printcp(Model1.RPart)
rpart.plot(Model1.RPart,
           type = 0,
           fallen.leaves = TRUE,
           uniform = TRUE,
           yes.text = "TRUE",
           no.text = "FALSE",
           cex = .8)

```

* Running a logistic regression

```{r}
Model2.LogReg <- glm(formula = lost ~ 
                         eopenrate
                         +eclickrate
                         +avgorder
                         +ordfreq
                         +paperless
                         +refill
                         +doorstep
                         +favday
                         +city
                         +cust_period,
                        data = filter(Retention2017, Sample == "Estimation"),
                        family = binomial(logit))
summary(Model2.LogReg)

```

* Running a stepwise regression

```{r}
Model3.StepReg <- step(Model2.LogReg, direction = "both")
summary(Model3.StepReg)
```

* Running a neural network

```{r}
Model4.NeuNet <- nnet(formula = lost ~ 
                        eopenrate
                        +eclickrate
                        +avgorder
                        +ordfreq
                        +paperless
                        +refill
                        +doorstep
                        +favday
                        +city
                        +cust_period,
                       data = filter(Retention2017, Sample == "Estimation"),
                       decay = 0.10, # decay parameter
                       size = 2)
Model4.NeuNet$value
summary(Model4.NeuNet)
```

* Running a random forest

```{r}
# Not working due to missing values
Model5.RanFor <- randomForest(formula = lost ~ 
                              eopenrate
                              +eclickrate
                              +avgorder
                              +ordfreq
                              +paperless
                              +refill
                              +doorstep
                              +favday
                              +city
                              +cust_period,
                              data = filter(Retention2017, Sample == "Estimation"),
                              importance = TRUE,
                              ntree = 500, mtry = 4)
Model5.RanFor
importance(Model5.RanFor,type = 2)
varImpPlot(Model5.RanFor,type = 2, main = "Importance Plot")

```

## Model Assessment Interpretation

* Building a cumulative captured lift chart

```{r}
# Error: could not find "lift.chart"
lift.chart(modelList = c("Model1.RPart", "Model2.LogReg", "Model3.StepReg", "Model4.NeuNet","Model5.RanFor"),
           data = filter(Retention2017, Sample == "Estimation"),
           targLevel = "Y",
           trueResp = 4749/(30729-7685),
           type = "cumulative", sub = "Estimation")

```

* Building an incremental captured lift chart

```{r}
# Error: could not find "lift.chart"
lift.chart(modelList = c("Model4.NeuNet"),
           data = as.data.frame(filter(Retention2017, Sample == "Validation")),
           targLevel = "Y",
           trueResp = 4749/(30729-7685),
           type = "incremental", sub = "Validation")

```

* Effect Plot for Logistic Regression

```{r}
plot(allEffects(Model2.LogReg),type = "response")
```

* Partial Dependence Plot for Random Forests

```{r}
partialPlot(Model5.RanFor,
            pred.data = as.data.frame(filter(Retention2017, Sample == "Validation")),
            x.var = eopenrate,
            sub = "Validation Set", 
            which.class = "Y")

```


## Scoring the prediction

* Generate predicted probability

```{r}
Retention2017$lost.Model1.RPart <- BCA::rawProbScore(model = "Model1.RPart",
                                           data = Retention2017,
                                          targLevel = "Y")
Submission.Model1.RPart <- Retention2017[Retention2017$Sample == "Holdout",c("custid","lost.Model1.RPart")]
names(Submission.Model1.RPart) <- c("custid", "score")
write.csv(Submission.Model1.RPart,"Submission.Model1.RPart.csv")
```