---
title: "Lab 6"
professor: "Brad McNeney"
edited by: "Nabila Doctor"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning=FALSE,message=FALSE)
```

```{r}
library(tidyverse)
library(nycflights13)
```

In this lab we will work with the `nycflights13` data.

1. Add the latitude and longitude of each 
airport destination to the `flights` table.
You will find the data on latitude and longitude
in the `airports` table.

```{r}
##flights
##airports

lat_lon <- airports %>% rename(origin=faa) %>% select(origin,lat,lon)
flights <- flights %>% full_join(lat_lon)
flights
```


2. Create a table with the
year-month-day-flight-tailnum
combinations that have more than 1 flight (careful about
missing tailnum). 
Use this table to filter the flights
table and then select carrire, flight, origin and dest.
Which airline used the same flight number for a plane
that made a trip from La Guardia to St. Louis in 
the morning and from Newark to Denver in the afternoon.

```{r}
flightsA <- flights %>% count(year,month,day,flight,tail_num) %>% filter(n>1,!is.na(tail_num))
flightsA

flights%>% semi_join(flightsA) %>% select(year:day,carrier,flight,origin,dest)
```


3. One of the exercises in the lecture 7 notes asked you
to create a table called `top_dep_delay` from
the flights table. 
`top_dep_delay` was
comprised of the year-month-days with the 
3 largest total delays, where total delay
is defined as the sum of the `dep_delay` variable
for each year-month-day. 
Recreate `top_dep_delay` for this lab exercise.
For each of the three top-delay days, 
report the median, third quartile and maximum
of the dep_delay variable in `flights`.

```{r}
(top_dep_delay <- flights %>% 
  group_by(year,month,day) %>% 
  summarize(tot_delay=sum(dep_delay,na.rm = TRUE)) %>% 
  arrange(desc(tot_delay)))
```

