---
title: "Lab 8"
professor: "Brad McNeney"
edited by: "Nabila Doctor"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning=FALSE,message=FALSE)
```

```{r}
library(tidyverse)
library(forcats)
library(lubridate)
yvr <- read_csv("weatherYVR.csv")
yvr
```

In the above code chunk you read in **daily** weather
data from YVR in 2003.

1. Coerce the `Date/Time` variable to a date object
and rename it Date.

```{r}
yvr <- yvr %>% 
  mutate('Date/Time'= ymd(`Date/Time`)) %>% 
  rename('Date'='Date/Time')
yvr
```

2. Do a time series plot (with lines) 
of the daily maximum temperature by day.
Use 'Max Temp' column

```{r}
ggplot(yvr,aes(x=`Date`,y=`Max Temp`)) + geom_line()
```

3. Change the `Month` variable from 
numeric to a factor.
(Hint: The `month()` function with the `label=TRUE` will
extract the months from a date-time object.)

```{r}
yvr <- yvr %>% 
  mutate('Month' = month(Month, label=TRUE))

yvr$Month <- factor(yvr$Month)

yvr
```

4. Plot the (y) average maximum temperature *versus* (x) month,.
Redo this plot with months ordered by 
average maximum.

```{r}
yvr %>% 
  summarize(mean = weighted.mean('Max Temp',Month,na.rm=TRUE)) %>%
  ggplot(aes(x=`Month`,y=mean)) + geom_point()
```
