---
title: "Lab 9"
professor: "Brad McNeney"
edited by: "Nabila Doctor"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning=FALSE,message=FALSE)
```

```{r}
library(tidyverse)
```

The folder `Lab9Data` contains several CSV files.
Each file contains an ID variable and a variable `res`  that 
holds results of an experiment on the study subjects.
You can obtain a vector with the file path and names with

```{r}
dfiles <- dir("Lab9Data",full.names=TRUE)
dfiles
```

1. Read the first datafile into a tibble named
`ex_data`. Change the name of the `res` column 
to `experiment1`, by manipulating the `names` attribute
of `ex_data`. That is, use `names(ex_data)[2] <- "experiment1"`.

```{r}
ex_data <- read_csv(dfiles[1]) 
names(ex_data)[2] <- "experiment 1"

ex_data
```


2. Write a function `read_ex()` that takes `dfiles`
and an experiment number `i` as arguments and returns
a tibble with the name of the `res` column
changed to the expermiment number. That is,
`read_ex(dfiles,1)` should
return the same tibble as in question 1.

```{r}
read_ex <- function(filename, exp_num) {
  ex_data <- read_csv(filename[exp_num]) 
  names(ex_data)[2] <- paste("experiment", exp_num)
  return(ex_data)
}

ex_data <- read_ex(dfiles,1)
ex_data
```


3. Use your function from question 2 to 
read in the second data file. Join this second file to 
`ex_data` by `ID.

```{r}
##ex_data <- read_ex(dfiles,2) %>% left_join(ex_data)
##left_join(ex_data,read_ex(dfiles,2),by="ID")
left_join(ex_data,read_ex(dfiles,2))
##ex_data
```

4. Write a function called `read_ex_data()` that
takes a folder name as its argument and 
    1. reads in the data filenames from that folder,
    2. calls `read_ex()` to read the first datafile into 
    `ex_data`,
    3. loops through the remaining data files, successively
    joining them to `ex_data`, and
    4. returns `ex_data`.

```{r}
read_ex_data <- function(folder) {
  dfiles <- dir(folder,full.names=TRUE)
  
  for (i in length(dfiles)) {
    if (i==1) {ex_data <- read_ex(dfiles,i)}
    else {ex_data <- read_ex(dfiles,i) %>% left_join(ex_data)}
  }
  
  for(i in seq_along(dfiles)){ if(i>1) { ex_data <- left_join(ex_data,read_ex(dfiles,i)) } }
  
  return(ex_data)
}

tt <- read_ex_data("Lab9Data")
tt
```

